Data Analytics Introduction Using Python Training

### 2024-11-08 MsaPythonDataAnalytics.qmd
update 2

---
title: "Data Analytics Introduction Using Python Training"
jupyter: python3
format: 
  revealjs:
    theme: serif
    smaller: true
    scrollable: true
    incremental: true
    transition: zoom
    background-transition: fade
code-fold: true
---

@@

@@

**Numbers**
**Integer Numbers**

@@

Immutable ordered sequence of items.

@@

@@

>>>>

---
title: "Data Analytics Introduction Using Python Training"
jupyter: python3
format: 
  revealjs:
    theme: serif
    smaller: true
    scrollable: true
    incremental: false
    transition: concave
    background-transition: fade
    controls: true
    code-fold: true
    code-tools: true

---

@@

Assigning objects to names **variables**

department = "DT"

print(department)

# you can change the variable on the fly

department = 'Customs'

print(department)
```

@@

**Numbers**

Integers, floating point numbers and complex numbers falls under Python numbers category.

> We can use the `type()` function to know which class a variable or a value belongs to and the `isinstance()` function to check if an object belongs to a particular class.

a = 5
print(a, "is of type", type(a))

a = 2.0
print(a, "is of type", type(a))

a = 1+2j
print(a, "is of type", type(a))
print(a, "is complex number?", isinstance(1+2j,complex))

@@

Immutable ordered sequence of items.Tuples once created cannot be modified.

@@

## Modules introduction

When our program grows bigger, it is a good idea to break it into different modules.

A module is a file containing Python definitions and statements. Python modules have a filename and end with the extension .py.

Definitions inside a module can be imported to another module or the interactive interpreter in Python. We use the import keyword to do this.

For example, we can import the math module by typing in import math.

import math
print(math.pi)

Checking paths using **sys** module

import sys
print(sys.path)
```

@@

### Matplotlip

Matplotlib is the "grandfather" library of data visualization with Python. It was created by John Hunter. He created it to try to replicate MatLab's (another programming language) plotting capabilities in Python. So if you happen to be familiar with matlab, matplotlib will feel natural to you.

It is an excellent 2D and 3D graphics library for generating scientific figures.

Some of the major Pros of Matplotlib are:

* Generally easy to get started for simple plots
* Support for custom labels and texts
* Great control of every element in a figure
* High-quality output in many formats
* Very customizable in general

Matplotlib allows you to create reproducible figures programmatically. Let's learn how to use it! Before continuing this lecture, I encourage you just to explore the official Matplotlib web page: [http://matplotlib.org/](http://matplotlib.org/)

```{python}
#| echo: true
#| eval: true
import matplotlib.pyplot as plt
```

```{python}
#| echo: true
import numpy as np
x = np.linspace(0, 5, 11)
y = x ** 2
```

Since we are using ipython notebook we need to run `%matplotlib inline` before running the plot

```{python}
#| echo: true
plt.plot(x, y, 'r') # 'r' is the color red
plt.xlabel('X Axis Title Here')
plt.ylabel('Y Axis Title Here')
plt.title('String Title Here')
plt.show()
```

### Seaborn
